### 2014-06-19 ms/ms.Rmd
MS: imporve study descriptions: lat,lon, methods, citations

```{r,results="asis",echo=FALSE, message=FALSE}
details2B  <-  daply(data, .(studyName), function(x)class2Bdetails(x))
writeLines(details2B,sep="\n\n")
```

>>>>

```{r,results="asis",echo=FALSE, message=FALSE}
library(plyr)
library(whisker)
details2B  <-  daply(data, .(studyName), function(x) studyDetails(x))
writeLines(details2B,sep="\n\n")
```
